\LARGE{Approximate Code: A Cost-Effective Erasure Code for MultimediavApplications in Cloud Storage Systems}\\

### 2019-03-25 paper.tex
version 0.2.2.0

Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application. For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to. Therefore, the encoded video data has an uneven degree of importance, that is, it is tolerable that some of those less important data losses because the users are hard to detect. On the other hand, loss of important data will have more serious consequences.

@@

\subsection{Our Motivation}
Based on Table 1, the existing erasure codes cannot meet the requirements of video applications in the cloud storage system due to the following reasons. First, existing erasure codes generally reach or exceed 3DFTS, and use more than 3 parity disks. However, the simultaneous damage of 3 disks is very rare, and the storage overhead paid for this is too large. Second, the existing erasure codes provide the same fault tolerance for all data without distinction, which results in the same reliability of important data that is sensitive to errors and data that is robust. To solve these two problems, we propose a new erasure code called approximation code. It provides different fault tolerance between important and non-critical data to reduce storage overhead and protect critical data better.

>>>>

Videos are typically stored in lossy compression, so they are subject to a certain quality loss when stored compared to the original version, and the extent of this quality loss can be specified by the application. For high-quality coded video, it is difficult for the human eye to distinguish the difference between them and the original video, because they preserve most of the brightness information, which human eye is very sensitive to, and some color information is discarded, which human eye is not sensitive to. Therefore, the encoded video data has an ununiform degree of importance, that is, it is tolerable that some of those less important data losses because the user is hard to detect.

@@

\subsection{Our Motivation}
